The Adaptive Multi-scale Simulation Infrastructure - Design and Application

### 2016-01-10 doc/articles/amsi_biotissue/paper.tex
work on the paper

@@

\section{Results and Discussion}\label{results}
The biotissue simulation was run on the AMOS BG/Q machine housed at the CCI facilities. Both strong and weak scaling studies were conducted up to an eighth of the total machine core count, or 16384 cores. The ratio of macro-scale to micro-scale assigned processes was held near 1:128, though the total core count was kept as an integer power of 2 in order for the SLURM job scheduler to submit the jobs to the compute nodes in a timely manner. The precise calculation used to determine macro and micro ratio is given by 
%
num_macro = N 
num_cores = N*128
num_micro = num_cores - N
%
thus as the number of cores assigned to the macro-scale computation increases, the ratio approaches 1:128.

@@

\begin{figure}
  \begin{center}
    \includegraphics[height=2in]{ws_phil.eps}
  \end{center}
  \caption{\small weak scaling}
  \label{biotissue_hierarchy}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[height=2in]{ss_phil.eps}
  \end{center}
  \caption{\small strong scaling}
  \label{biotissue_hierarchy}
\end{figure}

As the problem size is held constant with respect to the number of individual elements in the engineering scale domain discretization the simulation displays near optimal convergence to the macro-scale solve time alone, which is also reducing in time cost. The limiting factor in the speedup of the overall simulation is the potential speedup of the macro-scale simulation rather than the micro-scale simulation with fiber-only RVEs. As indicated in the weak scaling results this is related primarily to the macro-scale linear solve communication time increasing. At present an incomplete LU factorization is used to solve the linear system formulated at macro-scale each Newton iteraion (using PETSc configured with the superLU_dist solver \cite{li05superlu} \cite{lishao10superluilu} \cite{lidemmel03superludist} ). Using instead an iterative solution method to reach a desired level of accuracy may result in stronger scaling at macro-scale, but as yet this approach has been unneeded due to the preponderance of time spent computing micro-scale results in use cases.

>>>>

\section{Methods}

@@

\section{Results and Discussion}\label{results}
The biotissue simulation was run on the AMOS BG/Q machine housed at the CCI facilities. Both strong and weak scaling studies were conducted up to an eighth of the total machine core count, or 16384 cores. The ratio of macro-scale to micro-scale assigned processes was held near 1:128, though the total core count was kept as an integer power of 2 in order for the SLURM job scheduler to submit the jobs to the compute nodes in a timely manner. The precise calculation used to determine macro and micro ratio is given by 
%
num\_macro = N 
num\_cores = N*128
num\_micro = num\_cores - N
%
thus as the number of cores assigned to the macro-scale computation increases, the ratio approaches 1:128.

@@

\begin{figure}
  \begin{center}
    \includegraphics[height=2in]{ws_phil.eps}
  \end{center}
  \caption{\small weak scaling}
  \label{weak scaling}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[height=2in]{ss_phil.eps}
  \end{center}
  \caption{\small strong scaling}
  \label{strong scaling}
\end{figure}
As the problem size is held constant with respect to the number of individual elements in the engineering scale domain discretization the simulation displays near optimal convergence to the macro-scale solve time alone, which is also reducing in time cost. The limiting factor in the speedup of the overall simulation is the potential speedup of the macro-scale simulation rather than the micro-scale simulation with fiber-only RVEs. As indicated in the weak scaling results this is related primarily to the macro-scale linear solve communication time increasing. At present an incomplete LU factorization is used to solve the linear system formulated at macro-scale each Newton iteraion (using PETSc configured with the superLU\_dist solver \cite{li05superlu} \cite{lishao10superluilu} \cite{lidemmel03superludist} ). Using instead an iterative solution method to reach a desired level of accuracy may result in stronger scaling at macro-scale, but as yet this approach has been unneeded due to the preponderance of time spent computing micro-scale results in use cases.
